### 2022-02-16 ms/PrestigeBias.tex
update

\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}          
\usepackage{graphicx}
\usepackage{amsthm, amsmath, amssymb}
\usepackage[font=small]{caption, subcaption}
\usepackage{setspace}\onehalfspacing
\usepackage[loose,nice]{units}
\usepackage{array}
\usepackage[super]{nth}
\usepackage{graphicx}
\usepackage{float}
\usepackage{subcaption}
\usepackage{mathtools}
\usepackage[displaymath, mathlines]{lineno}
\usepackage{natbib}
\usepackage[all]{nowidow}
\usepackage{wrapfig}
\usepackage{pdfpages}
\newenvironment{conditions}
  {\par\vspace{\abovedisplayskip}\noindent\begin{tabular}{>{$}l<{$} @{${}={}$} l}}
  {\end{tabular}\par\vspace{\belowdisplayskip}}
\newcommand{\R}{\mathbb{R}}  
\DeclareMathOperator*{\E}{\mathbb{E}}

@@

The probability that the $i$-th copier chose role-model $j$
\begin{equation}\label{eq:recPrestige}
G_{i,j}=P(S_{i,j}=1| S_{1,j},S_{2,j},...,S_{i-1,j})
\end{equation}
is the prestige of role-model $j$ in the eyes of copier $i$.
This prestige $G_{i,j}$ is determined as follows.
First, role-model~$j$ is characterized by its indicator value $A_j$ as before, and the estimated indicator value by copier $i$, $A_{i,j}$ remains as Eq. \ref{eq:relativeIndicator}.
Finally, the prestige $G_{i,j}$ of role-model~$j$ in the eyes of copier~$i$ is determined by the estimated biased indicator value $\beta(A_{i,j})$ and the number of copiers that chose role-model $j$ before copier $i$, $K_{i-1,j}$, 
\begin{equation}\label{prestige_eq}
G_{i,j} = \frac{\alpha_j \cdot \beta(A_{i,j}) + (1-\alpha_j) \cdot K_{i-1,j}}{W_i},
\end{equation}
where the weight $\alpha_j$ is a characteristic of role-model~$j$ that determines the relative significance of the indicator and the influence in the prestige, and $W_i$ is a normalizing factor to ensure $\sum_{j=1}^N{G_{i,j}}=1$,
\begin{equation}
W_i = \sum_{j=1}^N{\Big(\alpha_j \cdot \beta(A_{i,j}) + (1-\alpha_j) \cdot K_{i-1,j}\Big)}.
\end{equation}

\subsection{Binary model} The indicator trait can now manifest in only two phenotypes, and for simplicity we define they can be either $\hat{A}$ or $A$. In the binary model, the influence is determined by the number of copiers already chosen \textbf{any} role-model with either $A$ or $\hat{A}$, as all role-models with $A$ will contribute to the probability of the trait to be inherited just the same (can be proved with simple induction). Simply put, assuming there are two role-models with the $A$ trait, the probability a copier will copy from either role-model will be the same, and the probability the $A$ trait will be inherited is the sum of both role-models.
In the general case, the probability of the $i$-th individual to inherit trait $A$, based on eq.\ref{copier_choose} is:
\begin{equation}\label{eq:binary-model}
P_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_A}{i-1 + (N-X)\alpha'\beta(A) + X\alpha'\beta(\hat{A})} = \frac{(N-X)\alpha'\beta(A) + K_A}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X}
\end{equation}
where $X$ is the number of role-models with trait $\hat{A}$ and $K_A$ is the number of copiers that already chose $A$.\\
The model begins with the first generation having a single individual with $\hat{A}$, and the rest have $A$. The process itself is the same stochastic process as the continuous model.

@@

\section{Results}
\subsection{Approximations}
Currently $\big\{\vec{K}_i\big\}_{i=1}^N$ is a stochastic process where each state depends on the previous state, i.e a Markov chain.
We wanted to find an equivalent stochastic process that has the same joint distribution on $\big\{\vec{K}_i\big\}_{i=1}^N$, but it is possible to evaluate the joint distribution directly without evaluating all the marginal conditional distributions (eq. \ref{eq:recurrence},\ref{eq:recPrestige}).

We found two approximations to our process, which are summarized here and explained in detail later on:
\begin{enumerate}
\item 
$K_{i,j}$ follows the general binomial distribution defined by \citet{GBD}.
Moreover, $\mathbb{E}[K_{N,j}] = N \cdot G_{1,j}$ if $e=e_l=e_m$ for all $l,m$.
 That is, the expected number of copiers of role-model~$j$ equals its prestige in the eyes of the first copier, multiplied by the total number of copiers. 
 In addition, we find that when $\alpha$ is homogeneous, $\alpha_l=\alpha_m$ for all $l,m$, then $\mathbb{E}[K_{N,j}] = \beta(A'_j) \; / \; \overline{\beta(A') }$, where $A'_j$ is the estimated indicator value $A'_j=A_j+e$, and 
 $\overline{ \beta(A') }$ is the population mean estimated indicator value. 
 That is, the expected number of copiers of a role-model equals its relative biased indicator value, similar to the role of relative fitness in population-genetic models.
\item The role-model choice process (equation~\ref{eq:process}) is equivalent to a P\'{o}lya urn model if $e_l=e_m$ for all $l,m$. 
Therefore, $\vec{K}_i = (K_{i,1}, \ldots, K_{i,N})$ follows a Dirichlet-Multinomial distribution,
\begin{equation}
\vec{K}_i \sim \mathit{DM}\big(N, \vec{G}_1\big), 
\end{equation}
where $\vec{G}_1 = (G_{1,1}, \ldots, G_{1,N})$.
Note that here $G_{i,j}$ is only a function of the indicator values $A_j$ and the weights $\alpha_j$.
\end{enumerate}

\subsection{General Binomial Distribution Approximation}
The general binomial distribution (GBD) is achieved by a series of Bernoulli experiments, with possible dependency between experiments.
\paragraph{Proposition:} The number of copiers $K_{i,j}$ follows the GBD, $K_{i,j} \sim GBD(i,\alpha_i\cdot\beta(A'_j))$, when $e_l=e_m$ for all $l,m \in N$ and $A'_j=A_j + e$ 
\paragraph{Proof: } We'll denote $Q_j(k,i)=P(K_{i,j} = k | K_{i-1,j})$ as the probability that exactly $k$ out of $i$ copiers choose role-model $j$, using conditional probability and equation \ref{eq:recurrence}:
\begin{equation}\label{recursive}
Q_j(k,i) = P_j(S_{i,j}=1 | k-1,i-1) \cdot Q_j(k-1,i-1) + P_j(S_{i,j} =0 | k,i-1) \cdot Q_j(k,i-1)
\end{equation}
where $S_{i,j} =1 $ when the $i$-th copier chooses role-model $j$.

Equation \ref{recursive} is equivalent to equation 2.1 that \citet{GBD} define.
$Q_j(k,N)$ is the probability that $k$ out of $N$ copiers choose role-model $j$ at the end of the process, which by our previous notation is $k=K_{N,j}$.
By describing the process of equation \ref{eq:process} as \citep{GBD} did, we've completed the proof.

@@

\paragraph{Corollary 2: } $\mathbb{E}[K_{Nj}] = \alpha_j \cdot \beta(A'_j) / \overline{\alpha \cdot \beta(A')}$.
\paragraph{Proof: } The initial prestige of role-model $j$ based on equation \ref{prestige_eq} is:
\begin{equation}\label{initial_prob}
G_{1,j} = \frac{\alpha_j\cdot\beta(A'_j)}{\sum\limits_{m=1}^{N}\alpha_m\cdot\beta(A'_m)}
\end{equation}
The denominator of equation \ref{initial_prob} can also be formulated as:
\begin{equation}\label{denominator}
 \sum\limits_{m=1}^{N}\alpha_m\beta(A'_m) = N \cdot \overline{\alpha \cdot \beta(A')}
\end{equation}
where $\overline{\alpha\beta(A')}$ is the mean value of $\alpha_m\cdot\beta(A'_m)$ for all $m$.
Using equation \ref{denominator} we get:
\begin{equation}
\mathbb{E}[K_{Nj}] = \alpha_j \cdot \beta(A'_j) \bigg/ \overline{\alpha \cdot \beta(A')}
\end{equation},
completing our proof.

@@

\paragraph{Proposition:} process $\big\{\vec{K}_i\big\}_{i=1}^N$ is equivalent to a \textit{Pólya urn model} when $e=e_i=e_j$ and $\alpha=\alpha_j=\alpha_i$ for all $i,j \in N$.
\paragraph{Proof:} 
We denote $\alpha'$ as the odds ratio between the weights of the indicator and the influence ($\alpha'=\frac{\alpha}{1-\alpha}$). 
Using equation \ref{prestige_eq} we get:
\begin{equation}\label{copier_choose}
\begin{split}
G_{i,j} & = \frac{\alpha\cdot \beta(A'_j) + (1-\alpha) \cdot K_{i-1,j}}{W_i} \cdot \frac{1-\alpha}{1-\alpha} \\\\
&= \frac{\alpha'\beta(A'_j) + K_{i-1,j}}{\sum\limits_{m=1}^{N} \alpha'\beta(A'_m) + K_{i-1,m}}\\\\
& =\frac{\alpha'\beta(A'_j) + K_{i-1,j}}{i-1 + \sum\limits_{m=1}^{N} \alpha'\beta(A'_m)}
\end{split}
\end{equation}
Equations \ref{polya} and \ref{copier_choose} are equivalent when setting $M=N$, $o_j = \alpha'\beta(A'_j)$, $w_{i,j} = K_{i,j}$, completing the proof.

@@

\paragraph{Numeric validation:} We showed our process is DM (Dirichlet-Multinomial) distributed when there are no errors when copying or evaluating the traits, and when $\alpha$ is homogeneous in the population. To test if our process is still DM distributed when there are copying errors in the population, we ran 400 simulations for three different error scales ($\eta$). To check the resemblance of the DM approximation to the original iterative process, we measure the $\chi^2$ statistic of both processes and the results can be seen in Fig. \ref{fig:chiSquaredHist}.
Even with a relatively high error scales (1\% and 10\% of J) we can see the distributions of the $\chi^2$ metrics are very similar.
With a higher $\eta$ (e.g $\eta=J$), which is approximately 100\% error when evaluating a trait, the distributions are noticeably different.

@@

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.3\textwidth}
    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_0_01.pdf}
    \subcaption{Error scale is 0.01}
    \end{subfigure}
    \begin{subfigure}[a]{0.3\textwidth}
    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_0_1.pdf} 
    \subcaption{Error scale is 0.1}
    \end{subfigure}
    \begin{subfigure}[a]{0.3\textwidth}
    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_J.pdf}
  \subcaption{Error scale is 1(=J)}  
  \end{subfigure}
  \caption{DM approximation vs iterative process. Population size 2000. 			Aggregated values of 400 simulations}	
  \label{fig:chiSquaredHist}
  \end{center}
\end{figure}

\subsection{Numeric comparisons}
We're interesting in studying the difference between the real binary model as we defined in eq. \ref{eq:binary-model}, and the Dirichlet-Multinomial approximation. Specifically, we're interesting in the fixation probability of the favored trait ($\hat{A}$) and its time to fixation.

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/num_sims.pdf}
  \caption{Population size $N=1000$, $\alpha=0.5$, $J=1$, $\hat{A}=1$,$A=0.7$, $\beta(A)=0.956$}	
  \label{fig:num_sims}
\end{figure}

The first step was to find the number of simulations needed to sufficiently approximate the real model with the DM approximation. From fig. \ref{fig:num_sims} we see that $1000$ simulations or higher is enough.

The next step was to see how the observed metrics (fixation probability and time) varies when relaxing our assumptions we used to prove the DM approximation.
First we relaxed our assumption of no mutation. To include mutation in the binary model, it needs to be redefined, since in the original model it was based on the fact the traits are drawn from a continuous scale. In the binary model mutation will be manifested as an error when evaluating the bias itself. This is easily done by using a heterogeneous $J$ parameter, which controls the strength of the success bias (see eq. \ref{eq:success_bias}).

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_mutation.pdf}
  \caption{$5000$ simulations per data point, $N=1000$, $\alpha=0.1$,$\hat{A}=1$,$A=0.7$, $J\sim N(1,x^2)$ where $x$ is the mutation scale in the x-axis}	
  \label{fig:hetro_mutation}
\end{figure}

In fig. \ref{fig:hetro_mutation} we see the comparison when heterogeneous mutation is applied to both models. When mutation is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance).
We can see that even when the standard deviation is $0.1$, the metrics of both models are both similar, and close to the Kimura approximation (more details in the next section).

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_changing_alpha.pdf}
  \caption{$5000$ simulations per data point, $N=1000$, $\alpha\sim N(0.5,x^2)$,$\hat{A}=1$,$A=0.7$, $J=1$, $\beta(A)=0.956$}	
  \label{fig:hetro_alpha}
\end{figure}

In fig. \ref{fig:hetro_alpha} we relaxed our assumption of a homogeneous $\alpha$, and used a heterogeneous $\alpha$ instead. Similar to the mutation comparison, we drew $\alpha_j$ for each role-model $j$ from a normal distribution with varying scale. We again see that the metrics of both models are similar in the entire spectrum of our x-axis, and the Kimura approximation is within both confidence intervals.

\subsection{Fixation probability and time - binary model}
\paragraph{Kimura's approximation:}
After establishing a case in the favor of our DM approximation, we wanted to use it to examine the behavior of the population. Specifically, we wanted to analyze the influence of the indicator weight ($\alpha$) on the fixation probability and time to fixation of the favored phenotype in a binary model.
For simplicity, we don't include mutation rate in the binary model approximations.
Following \citet{durret}, we used our DM approximation of the model to find the effective population size. From eq. \ref{eq:binary-model} we can derive that the process of inheritance in our binary model is DM distributed with a parameters vector of size two: $\vec{V}=(\alpha'X,(N-X)\alpha'\beta(A))$.

@@

The expected number of individuals of a DM distribution is:
\begin{equation}
E[X'] = N  \frac{\alpha_1}{\alpha_1+\alpha_2},
\end{equation}
where $\alpha_1 = \alpha' X$ and $\alpha_2 = \alpha'(N-X)\beta$, from eq. \ref{eq:binary-model}.
We want to use frequencies instead of quantities to follow Durret's process so:
\begin{equation}
E[x'] = E[\frac{X'}{N}] = \frac{1}{N}E[X']
\end{equation}
Putting it together we get:
\begin{equation}
\begin{split}
E[x'] &= \frac{1}{N}N\frac{\alpha' xN}{\alpha' xN + \alpha' N (1-x)\beta}\\\\
	 &= \frac{x}{x + (1-x)\beta}
\end{split}
\end{equation}

@@

To validate our math we ran multiple simulations comparing our binary model with the classic Wright-Fisher model, using different $\alpha$ and $\beta$ each time, and using the corresponding values of $s$ and $N_e$ for the WF simulations.
In fig \ref{fig:var_alpha} we changed $\alpha$ (and $N_e$ accordingly) and used a constant $\beta$.
In fig \ref{fig:var_beta} we changed $\beta$ and used a constant $\alpha$.
In both cases we can see that the two models behave similarly, and both are approximated well by the Kimura's equations (eq. \ref{eq:kimura_p} and \ref{eq:kimura_t})

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_alpha.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_alpha.pdf}
   \end{subfigure}
  \end{center}
  \caption{$5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$1-\beta=0.044$}
  \label{fig:var_alpha}
\end{figure}

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_beta.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_beta.pdf}
   \end{subfigure}
  \end{center}
  \caption{$5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$\alpha=0.01$}
  \label{fig:var_beta}
\end{figure}

@@

Using the induction assumption and eq.\ref{eq:ch_var2}:
\begin{equation}
V\left(\frac{X_{t+1}}{N}\right) \simeq \frac{1}{N_e}x(1-x) + \frac{1}{N_e}tx(1-x) \simeq \frac{1}{N_e}x(1-x)(t+1)
\end{equation}
proving the second part of our preposition.

>>>>

\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}          
\usepackage{graphicx}
\usepackage{amsthm, amsmath, amssymb}
\usepackage[font=small]{caption, subcaption}
\usepackage{setspace}\onehalfspacing
\usepackage[loose,nice]{units}
\usepackage{array}
\usepackage[super]{nth}
\usepackage{graphicx}
\usepackage{float}
\usepackage{cleveref}
\usepackage{subcaption}
\usepackage{mathtools}
\usepackage[displaymath, mathlines]{lineno}
\usepackage{natbib}
\usepackage[all]{nowidow}
\usepackage{wrapfig}
\usepackage{pdfpages}
\newenvironment{conditions}
  {\par\vspace{\abovedisplayskip}\noindent\begin{tabular}{>{$}l<{$} @{${}={}$} l}}
  {\end{tabular}\par\vspace{\belowdisplayskip}}
\newcommand{\R}{\mathbb{R}}  
\DeclareMathOperator*{\E}{\mathbb{E}}

@@

The probability that the $i$-th copier chose role-model $j$
\begin{equation}\label{eq:recPrestige}
G_{i,j}=P(S_{i,j}=1| S_{1,j},S_{2,j},...,S_{i-1,j})
\end{equation}
is the prestige of role-model $j$ in the eyes of copier $i$.
This prestige $G_{i,j}$ is determined as follows.
First, role-model~$j$ is characterized by its indicator value $A_j$ as before, and the estimated indicator value by copier $i$, $A_{i,j}$ remains as \cref{eq:relativeIndicator}.
Finally, the prestige $G_{i,j}$ of role-model~$j$ in the eyes of copier~$i$ is determined by the estimated biased indicator value $\beta(A_{i,j})$ and the number of copiers that chose role-model $j$ before copier $i$, $K_{i-1,j}$, 
\begin{equation}\label{prestige_eq}
G_{i,j} = \frac{\alpha_j \cdot \beta(A_{i,j}) + (1-\alpha_j) \cdot K_{i-1,j}}{W_i},
\end{equation}
where the weight $\alpha_j$ is a characteristic of role-model~$j$ that determines the relative significance of the indicator and the influence in the prestige, and $W_i$ is a normalizing factor to ensure $\sum_{j=1}^N{G_{i,j}}=1$,
\begin{equation}
W_i = \sum_{j=1}^N{\Big(\alpha_j \cdot \beta(A_{i,j}) + (1-\alpha_j) \cdot K_{i-1,j}\Big)}.
\end{equation}

\subsection{Binary model} The indicator trait can now manifest in only two phenotypes, and for simplicity we define they can be either $\hat{A}$ or $A$. In the binary model, the influence is determined by the number of copiers already chosen \textbf{any} role-model with either $A$ or $\hat{A}$, as all role-models with $A$ will contribute to the probability of the trait to be inherited just the same (can be proved with simple induction). Simply put, assuming there are two role-models with the $A$ trait, the probability a copier will copy from either role-model will be the same, and the probability the $A$ trait will be inherited is the sum of both role-models.
In the general case, the probability of the $i$-th individual to inherit trait $A$, based on \cref{copier_choose} is:
\begin{equation}\label{eq:binary-model}
P_{i,A} = \frac{(N-X)\alpha'\beta(A) + K_A}{i-1 + (N-X)\alpha'\beta(A) + X\alpha'\beta(\hat{A})} = \frac{(N-X)\alpha'\beta(A) + K_A}{i-1 + (N-X)\alpha'\beta(A) + \alpha'X}
\end{equation}
where $X$ is the number of role-models with trait $\hat{A}$ and $K_A$ is the number of copiers that already chose $A$.\\
The model begins with the first generation having a single individual with $\hat{A}$, and the rest have $A$. The process itself is the same stochastic process as the continuous model.

@@

\section{Results}
\subsection{Approximations}
Currently $\big\{\vec{K}_i\big\}_{i=1}^N$ is a stochastic process where each state depends on the previous state, i.e a Markov chain.
We wanted to find an equivalent stochastic process that has the same joint distribution on $\big\{\vec{K}_i\big\}_{i=1}^N$, but it is possible to evaluate the joint distribution directly without evaluating all the marginal conditional distributions: \cref{eq:recurrence}, \cref{eq:recPrestige}.

We found two approximations to our process, which are summarized here and explained in detail later on:
\begin{enumerate}
\item 
$K_{i,j}$ follows the general binomial distribution defined by \citet{GBD}.
Moreover, $\mathbb{E}[K_{N,j}] = N \cdot G_{1,j}$ if $e=e_l=e_m$ for all $l,m$.
 That is, the expected number of copiers of role-model~$j$ equals its prestige in the eyes of the first copier, multiplied by the total number of copiers. 
 In addition, we find that when $\alpha$ is homogeneous, $\alpha_l=\alpha_m$ for all $l,m$, then $\mathbb{E}[K_{N,j}] = \beta(A'_j) \; / \; \overline{\beta(A') }$, where $A'_j$ is the estimated indicator value $A'_j=A_j+e$, and 
 $\overline{ \beta(A') }$ is the population mean estimated indicator value. 
 That is, the expected number of copiers of a role-model equals its relative biased indicator value, similar to the role of relative fitness in population-genetic models.
\item The role-model choice process \cref{eq:process} is equivalent to a P\'{o}lya urn model if $e_l=e_m$ for all $l,m$. 
Therefore, $\vec{K}_i = (K_{i,1}, \ldots, K_{i,N})$ follows a Dirichlet-Multinomial distribution,
\begin{equation}
\vec{K}_i \sim \mathit{DM}\big(N, \vec{G}_1\big), 
\end{equation}
where $\vec{G}_1 = (G_{1,1}, \ldots, G_{1,N})$.
Note that here $G_{i,j}$ is only a function of the indicator values $A_j$ and the weights $\alpha_j$.
\end{enumerate}

\subsection{General Binomial Distribution Approximation}
The general binomial distribution (GBD) is achieved by a series of Bernoulli experiments, with possible dependency between experiments.
\paragraph{Proposition:} The number of copiers $K_{i,j}$ follows the GBD, $K_{i,j} \sim GBD(i,\alpha_i\cdot\beta(A'_j))$, when $e_l=e_m$ for all $l,m \in N$ and $A'_j=A_j + e$ 
\paragraph{Proof: } We'll denote $Q_j(k,i)=P(K_{i,j} = k | K_{i-1,j})$ as the probability that exactly $k$ out of $i$ copiers choose role-model $j$, using conditional probability and \cref{eq:recurrence}:
\begin{equation}\label{recursive}
Q_j(k,i) = P_j(S_{i,j}=1 | k-1,i-1) \cdot Q_j(k-1,i-1) + P_j(S_{i,j} =0 | k,i-1) \cdot Q_j(k,i-1)
\end{equation}
where $S_{i,j} =1 $ when the $i$-th copier chooses role-model $j$.

We see that \cref{recursive} is equivalent to eq. (2.1) that \citet{GBD} define.
$Q_j(k,N)$ is the probability that $k$ out of $N$ copiers choose role-model $j$ at the end of the process, which by our previous notation is $k=K_{N,j}$.
By describing the process of \cref{eq:process} as \citep{GBD} did, we've completed the proof.

@@

\paragraph{Corollary 2: } $\mathbb{E}[K_{Nj}] = \alpha_j \cdot \beta(A'_j) / \overline{\alpha \cdot \beta(A')}$.
\paragraph{Proof: } The initial prestige of role-model $j$ based on \cref{prestige_eq} is:
\begin{equation}\label{initial_prob}
G_{1,j} = \frac{\alpha_j\cdot\beta(A'_j)}{\sum\limits_{m=1}^{N}\alpha_m\cdot\beta(A'_m)}
\end{equation}
The denominator of \cref{initial_prob} can also be formulated as:
\begin{equation}\label{denominator}
 \sum\limits_{m=1}^{N}\alpha_m\beta(A'_m) = N \cdot \overline{\alpha \cdot \beta(A')}
\end{equation}
where $\overline{\alpha\beta(A')}$ is the mean value of $\alpha_m\cdot\beta(A'_m)$ for all $m$.
Using \cref{denominator} we get:
\begin{equation}
\mathbb{E}[K_{Nj}] = \alpha_j \cdot \beta(A'_j) \bigg/ \overline{\alpha \cdot \beta(A')}
\end{equation},
completing our proof.

@@

\paragraph{Proposition:} process $\big\{\vec{K}_i\big\}_{i=1}^N$ is equivalent to a \textit{Pólya urn model} when $e=e_i=e_j$ and $\alpha=\alpha_j=\alpha_i$ for all $i,j \in N$.
\paragraph{Proof:} 
We denote $\alpha'$ as the odds ratio between the weights of the indicator and the influence ($\alpha'=\frac{\alpha}{1-\alpha}$). 
Using \cref{prestige_eq} we get:
\begin{equation}\label{copier_choose}
\begin{split}
G_{i,j} & = \frac{\alpha\cdot \beta(A'_j) + (1-\alpha) \cdot K_{i-1,j}}{W_i} \cdot \frac{1-\alpha}{1-\alpha} \\\\
&= \frac{\alpha'\beta(A'_j) + K_{i-1,j}}{\sum\limits_{m=1}^{N} \alpha'\beta(A'_m) + K_{i-1,m}}\\\\
& =\frac{\alpha'\beta(A'_j) + K_{i-1,j}}{i-1 + \sum\limits_{m=1}^{N} \alpha'\beta(A'_m)}
\end{split}
\end{equation}
We see that \cref{polya} and \cref{copier_choose} are equivalent when setting $M=N$, $o_j = \alpha'\beta(A'_j)$, $w_{i,j} = K_{i,j}$, completing the proof.

@@

\paragraph{Numeric validation:} We showed our process is DM (Dirichlet-Multinomial) distributed when there are no errors when copying or evaluating the traits, and when $\alpha$ is homogeneous in the population. To test if our process is still DM distributed when there are copying errors in the population, we ran 400 simulations for three different error scales ($\eta$). To check the resemblance of the DM approximation to the original iterative process, we measure the $\chi^2$ statistic of both processes and the results can be seen in \cref{fig:chiSquaredHist}.
Even with a relatively high error scales (1\% and 10\% of J) we can see the distributions of the $\chi^2$ metrics are very similar.
With a higher $\eta$ (e.g $\eta=J$), which is approximately 100\% error when evaluating a trait, the distributions are noticeably different.

@@

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.3\textwidth}
  \subcaption{Error scale is 0.01}
    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_0_01.pdf}
    \end{subfigure}
    \begin{subfigure}[a]{0.3\textwidth}
    \subcaption{Error scale is 0.1}
    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_0_1.pdf} 
    \end{subfigure}
    \begin{subfigure}[a]{0.3\textwidth}
     \subcaption{Error scale is 1(=J)}
    \includegraphics[width=\linewidth]{../figures/chi_square_stats/chi_hist_homogenous_J.pdf}
  \end{subfigure}
  \caption{Demonstrates the similarities between the $\chi ^2$ metric of 	           the DM approximation and the full model, showing the approximation is good until a very high error rate. Population size $N=2000$. 400 simulations per figure}	
  \label{fig:chiSquaredHist}
  \end{center}
\end{figure}

\subsection{Numeric comparisons}
We're interesting in studying the difference between the real binary model as we defined in \cref{eq:binary-model}, and the Dirichlet-Multinomial approximation. Specifically, we're interesting in the fixation probability of the favored trait ($\hat{A}$) and its time to fixation.

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/num_sims.pdf}
  \caption{The number of simulations needed to get a good approximation. At $1,000$ the approximation is good enough. Error bars represent 95\% confidence interval. Population size $N=1000$, $\alpha=0.5$, $J=1$, $\hat{A}=1$,$A=0.7$, $\beta(A)=0.956$.}	
  \label{fig:num_sims}
\end{figure}

The first step was to find the number of simulations needed to sufficiently approximate the real model with the DM approximation. From \cref{fig:num_sims} we see that $1000$ simulations or higher is enough.

The next step was to see how the observed metrics (fixation probability and time) varies when relaxing our assumptions we used to prove the DM approximation.
First we relaxed our assumption of no mutation. To include mutation in the binary model, it needs to be redefined, since in the original model it was based on the fact the traits are drawn from a continuous scale. In the binary model mutation will be manifested as an error when evaluating the bias itself. This is easily done by using a heterogeneous $J$ parameter, which controls the strength of the success bias in \cref{eq:success_bias}.

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_mutation.pdf}
  \caption{Comparison of the DM approximation and the full model when mutation is included. Even high mutation rate doesn't worsen the approximation, and the data points are close to the mathematical estimation (Kimura's). Error bars are 95\% confidence intervals, and are condensed (+- 0.01 probability and +-40 generations)
  $5000$ simulations per data point, $N=1000$, $\alpha=0.1$,$\hat{A}=1$,$A=0.7$, $J\sim N(1,x^2)$ where $x$ is the mutation scale in the x-axis.
  }	
  \label{fig:hetro_mutation}
\end{figure}

In \cref{fig:hetro_mutation} we see the comparison when heterogeneous mutation is applied to both models. When mutation is applied, we sample $J_i$ for each copier $i$ from a normal distribution with varying scale (variance).
We can see that even when the standard deviation is $0.1$, the metrics of both models are both similar, and close to the Kimura approximation (more details in the next section).

\begin{figure}
    \includegraphics[width=\linewidth]{../figures/binary/full_vs_dm_changing_alpha.pdf}
  \caption{Comparison of the DM approximation and the full model when success weight is heterogeneous. High success weight variance distances the approximation and the full model of generations to fixation from the Kimura's approximation, but not by much (confidence intervals still cover it). Error bars are 95\% confidence intervals, and are less condensed (+- 0.03 probability and +-40 generations)
  $5000$ simulations per data point, $N=1000$, $\alpha\sim N(0.5,x^2)$,$\hat{A}=1$,$A=0.7$, $J=1$, $\beta(A)=0.956$.}	
  \label{fig:hetro_alpha}
\end{figure}

In \cref{fig:hetro_alpha} we relaxed our assumption of a homogeneous $\alpha$, and used a heterogeneous $\alpha$ instead. Similar to the mutation comparison, we drew $\alpha_j$ for each role-model $j$ from a normal distribution with varying scale. We again see that the metrics of both models are similar in the entire spectrum of our x-axis, and the Kimura approximation is within both confidence intervals.

\subsection{Fixation probability and time - binary model}
\paragraph{Kimura's approximation:}
After establishing a case in the favor of our DM approximation, we wanted to use it to examine the behavior of the population. Specifically, we wanted to analyze the influence of the indicator weight ($\alpha$) on the fixation probability and time to fixation of the favored phenotype in a binary model.
For simplicity, we don't include mutation rate in the binary model approximations.
Following \citet{durret}, we used our DM approximation of the model to find the effective population size. From \cref{eq:binary-model} we can derive that the process of inheritance in our binary model is DM distributed with a parameters vector of size two: $\vec{V}=(\alpha'X,(N-X)\alpha'\beta(A))$.

@@

The expected number of individuals of a DM distribution is:
\begin{equation}
E[X'] = N  \frac{\alpha_1}{\alpha_1+\alpha_2},
\end{equation}
where $\alpha_1 = \alpha' X$ and $\alpha_2 = \alpha'(N-X)\beta$, from  \cref{eq:binary-model}.
We want to use frequencies instead of quantities to follow Durret's process so:
\begin{equation}
E[x'] = E[\frac{X'}{N}] = \frac{1}{N}E[X']
\end{equation}
Putting it together we get:
\begin{equation}
\begin{split}
E[x'] &= \frac{1}{N}N\frac{\alpha' xN}{\alpha' xN + \alpha' N (1-x)\beta}\\\\
	 &= \frac{x}{x + (1-x)\beta}
\end{split}
\end{equation}

@@

To validate our math we ran multiple simulations comparing our binary model with the classic Wright-Fisher model, using different $\alpha$ and $\beta$ each time, and using the corresponding values of $s$ and $N_e$ for the WF simulations.
In \cref{fig:var_alpha} we changed $\alpha$ (and $N_e$ accordingly) and used a constant $\beta$.
In \cref{fig:var_beta} we changed $\beta$ and used a constant $\alpha$.
In both cases we can see that the two models behave similarly, and both are approximated well by the Kimura's equations: \cref{eq:kimura_p} and \cref{eq:kimura_t}.

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
    \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_alpha.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
     \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_alpha.pdf}
   \end{subfigure}
  \end{center}
  \caption{Comparison of the DM approximation and the WF model for different values of the effective population size. The approximation seems very good, and is also condensed around the mathematical equation expectancy. Error bars are 95\% confidence intervals.
  Effective population calculated by $N_e=\alpha N + (1-\alpha)$.
  $5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$1-\beta=s=0.044$.}
  \label{fig:var_alpha}
\end{figure}

\begin{figure}[t]
  \begin{center}
  \begin{subfigure}[a]{0.49\linewidth}
  \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_prob_var_beta.pdf}
   \end{subfigure}
   \begin{subfigure}[a]{0.49\linewidth}
    \caption{}
    \includegraphics[width=\linewidth]{../figures/binary/fix_time_var_beta.pdf}
   \end{subfigure}
  \end{center}
  \caption{Comparison of the DM approximation and the WF model for different values of the selection coefficient, manifested as success bias in our model. The approximation seems good, and is also condensed around the mathematical equation expectancy. Error bars are 95\% confidence intervals.
  Effective population calculated by $N_e=\alpha N + (1-\alpha)$.
  $5,000$ simulations per data point, $N=1,000$, $\hat{A}=1$, $A=0.7$,$J=1$,$\alpha=0.01$.}
  \label{fig:var_beta}
\end{figure}

@@

Using the induction assumption and \cref{eq:ch_var2}:
\begin{equation}
V\left(\frac{X_{t+1}}{N}\right) \simeq \frac{1}{N_e}x(1-x) + \frac{1}{N_e}tx(1-x) \simeq \frac{1}{N_e}x(1-x)(t+1)
\end{equation}
proving the second part of our preposition.
